---
output: 
  html_document:
    keep_md: TRUE
    variant: markdown_github
---

```{r readme-setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/readrbio)](http://cran.r-project.org/package=readrbio)
[![Travis-CI Build Status](https://travis-ci.org/npjc/readrbio.svg?branch=master)](https://travis-ci.org/npjc/readrbio)
[![Coverage Status](http://codecov.io/github/npjc/readrbio/coverage.svg?branch=master)](http://codecov.io/github/npjc/readrbio?branch=master)

### readrbio

`readrbio` is an R pkg that provides some wrappers around [`readr`](https://github.com/hadley/readr) for common file formats, such as the common biological formats `.gff3`, `.wig`, and `.bed` using a consistent extension mechanism.

```{r get-pkg, eval = FALSE}
# install.packages("devtools")
devtools::install_github("npjc/readrbio")
```



### How it wraps
`readrbio` is centered around `file_spec`ifications. This is simply a named list with a standard set of parameters. Specifically, the some or all of formals (arguments) for [readr's](https://github.com/hadley/readr) `read_delimited()`.

```{r file-spec}
library(readrbio)
file <- "my-file.tab2"
spec(file, type = "biogrid", "tab2i")
file <- "my-other-file.gff3"
spec(file, "gff", "gff3")
```

You can then modify a file spec with `infr_*` functions. For example, `infr_skip()`
will figure out how many rows to skip based on the expected number of fields and by ignoring rows that start with a certain pattern (`"#"` by default). The resulting modified `file_spec` is passed onto `do_read()` which will read in the file according to its specification, filling in any unspecified arguments with defaults if need be.
```{r infr-skip, eval=FALSE}
spec(file, "gff", "gff3") %>% 
  infr_skip() %>% 
  do_read()
```

### Exported
Pkg currently exports `r length(grep("export", readLines("NAMESPACE"), value = T))` functions:
```{r, echo = FALSE}
exports <- grep("export", readLines("NAMESPACE"), value = T)
unlist(lapply(strsplit(exports, "[(//)]"), `[`, 2))
```

The `%>%` operator is from [magrittr](https://github.com/smbache/magrittr).
